A Dearth of Young Stars and Planets in the Kepler Field

### 2024-05-22 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.99\textwidth]{olympic_merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Literature ages vs.~benchmark open cluster ages.}
		Each point denotes a reported age,
		normalized by the age of a stellar ensemble in which the star
		is a candidate member.
		We used candidate cluster members from previous studies that used spatial and kinematic
		information.  Although some field interlopers may be present in the 
		membership lists,
		any outliers can be compared between different methods on a
		relative basis.
		The number of stars in any given cluster follows by crossmatching every study against
		a fixed cluster list; certain methods report ages for more stars than others.
		Horizontal scatter is artificially added to visually
		clarify the statistical age uncertainties.
	}
	\label{fig:agescalecompone}
\end{figure*}

@@

In Figure~\ref{fig:agescalecompone}, we compare our rotation-based
ages, as well as select ages from the literature, against the ages of stars in the richest
clusters in the Kepler field.
From previous studies, we show ages from \citet{Berger_2020a_catalog},
\citet{2021AJ....161..189L}, \citet{2023ApJ...952..131M}, and
\citet{2024AJ....167..159L}.
We followed any guidance available from these respective studies for
removing ages that were explicitly flagged as unreliable, and plotted
stars within $1\sigma$ of zero as being upper limits.

Cluster memberships are a delicate subject.
Figure~\ref{fig:agescalecompone} is showing reported ages for
a set of spatially and kinematically selected set of stars that could be cluster members, or
they could be field interlopers.  For NGC6811 and NGC6819, we
adopted candidate members from
\citet{2018A&A...618A..93C,CantatGaudin_2020} and
\citet{Kounkel_2020}. 
For Melange-3 we used the candidates reported by
\citet{Barber_2022} and required ``offset'' tangential
velocities below 2\,\kms.  For Cep-Her we
used candidate members from Table~2 of \citet{Bouma_2022b}, requiring
``weights'' exceeding 0.1.
Even with contaminants, we can compare
the relative age distributions derived by the different studies because in all
instances we are comparing reported ages against a fixed list of stars.

@@

The point of Figure~\ref{fig:agescalecompone} is hopefully clear.
While previous studies have been able to derive accurate ages for
stars $\gtrsim$1\,Gyr old, the ages of sub-gigayear stars have historically been
overestimated by anywhere from 0.5--2\,dex.
The situation is particularly severe for the 40\,Myr stars in Cep-Her,
but it is also present for 150--300\,Myr stars in Melange-3 and Theia~520.
For isochrone and kinematic ages,
this is not surprising because these methods use stellar parameters that do
not appreciably change at $t$$\lesssim$1\,Gyr.
For the rotation-based ages quoted by
\citet{2023ApJ...952..131M} and \citet{2024AJ....167..159L}, the discrepancy
between their ages and the cluster age scale is likely caused by details of the calibration 
methodologies.
The physical spin-down models used by
\citet{2023ApJ...952..131M},
and the gyro-kinematic calibration ages used by \citet{2024AJ....167..159L},
may not reproduce
the rotation sequences of open clusters such as Praesepe, the Hyades, and the Pleiades.
The statistical age uncertainties yielded by these approaches
similarly may not marginalize over the intrinsic
scatter in rotation periods present in stars of a fixed mass at any given age.

%The rotation-based ages that we have calculated have a precision
%limited by the intrinsic scatter in the cluster rotation sequences.
%Within the age range accessible through the clusters, they seem to be
%mostly accurate,
%with the one exception being that our ages for stars in Cep-Her 
%have a typical median of $\approx$80\,Myr, rather than 40\,Myr.
%The reason is that 80\,Myr is the lower bound of 
%the \texttt{gyro-interp}  age grid; pre-main-sequence
%spin-up is outside of our calibration regime.

@@

\begin{figure*}[!t]
  \begin{center}
    \leavevmode
    \subfloat{
    \includegraphics[width=.99\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000.pdf}
    }

	\vspace{-0.35cm}
    \subfloat{
    \includegraphics[width=.99\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000_preciseagesonly.pdf}
    }
  \end{center}
  \vspace{-0.66cm}
  \caption{{\bf Kepler's demographic cliff,} visible in the
  rotation-derived ages of stars (left) and planet hosts (middle) in
  the Kepler field.  The top row corresponds to all stars with
  temperatures of 3800--6200\,K for which we calculated rotation-based
  ages.  The opaque lines impose quality cuts on factors such as
  binarity, crowding, and the star's evolutionary state.  The bottom
  row selects only stars with temperatures of 4400-5400\,K, which have
  relatively precise ages near 2\,Gyr due to their fast spin-down.
  The statistical uncertainty for a mean
  individual star at 1, 2, and 3\,Gyr is shown, and is identical
  across each row.  Finally, the right panel compares the
  rotation-derived ages against star formation histories
  derived using CMD fitting.  Completeness in Kepler's
  $P$$_{\rm rot}$ detection sensitivity is near unity until
  $t$$\lesssim$3\,Gyr \citep{2022ApJ...937...94M}.
  \label{fig:hist_tgyro}
  }
\end{figure*}

@@

\software{
  astropy \citep{Astropy18},
  matplotlib \citep{matplotlib},
  numpy \citep{numpy},
  scipy \citep{scipy},
}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{olympic_merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Literature ages vs.~benchmark open cluster ages.}
		Each point denotes a reported age,
		normalized by the age of a stellar ensemble in which the star
		is a candidate member.
		Cluster membership was assessed in previous studies without knowledge of rotation.
		Although some field interlopers may be present in the 
		membership lists,
		any outliers can be compared between different methods on a
		relative basis.
		The number of stars in any given cluster follows by crossmatching every study against
		a fixed cluster list; certain methods report ages for more stars than others.
		Horizontal scatter is artificially added to visually
		clarify the statistical age uncertainties.
	}
	\label{fig:agescalecompone}
\end{figure*}

@@

In Figure~\ref{fig:agescalecompone}, we compare our rotation-based
ages, as well as select ages from the literature, against the ages of
stars in the richest clusters in the Kepler field.  From the
literature, we drew ages from \citet{Reinhold_2015},
\citet{Berger_2020a_catalog}, \citet{2021AJ....161..189L},
\citet{2023ApJ...952..131M}, and \citet{2024AJ....167..159L}.  We
followed any guidance available from these respective studies for
removing ages that were explicitly flagged as unreliable, and plotted
stars within $1\sigma$ of zero as being upper limits.  For the
\citeauthor{Reinhold_2015} ages, we used those that were calculated
using the \citet{Mamajek_2008} calibration; for the
\citeauthor{2023ApJ...952..131M} ages, we show those from
\texttt{kiauhoku} \citep{Claytor2020} rather than \texttt{STAREVOL}
\citep{Amard2019}, based on the defaults adopted by
\citeauthor{2023ApJ...952..131M}.

Cluster membership is a delicate subject.
Figure~\ref{fig:agescalecompone} is showing reported ages for a set of
spatially and kinematically selected set of stars that could be
cluster members, or they could be field interlopers.  For NGC6811 and
NGC6819, we adopted candidate members from
\citet{2018A&A...618A..93C,CantatGaudin_2020} and
\citet{Kounkel_2020}.  For Melange-3 we used the candidates reported
by \citet{Barber_2022} and required ``offset'' tangential velocities
below 2\,\kms.  For Cep-Her we used candidate members from Table~2 of
\citet{Bouma_2022b}, requiring ``weights'' exceeding 0.1.  Even with
contaminants, we can compare the relative age distributions derived by
the different studies because in all instances we are comparing
reported ages against a fixed list of stars.

@@

The point of Figure~\ref{fig:agescalecompone} is hopefully clear.
While previous studies have been able to derive accurate ages for
stars $\gtrsim$1\,Gyr old, the ages of sub-gigayear stars have
historically been overestimated by anywhere from 0.3--2\,dex.  The
situation is particularly severe for the 40\,Myr stars in Cep-Her, but
it is also present for 150--300\,Myr stars in Melange-3 and Theia~520.
For isochrone and kinematic ages, this is not surprising because these
methods rely on parameters that do not appreciably change at
$t$$\lesssim$1\,Gyr.  For the rotation-based ages quoted by
\citet{2023ApJ...952..131M} and \citet{2024AJ....167..159L}, the
discrepancy is likely
caused by details of the calibration methodologies.  The physical
spin-down models used by \citet{2023ApJ...952..131M}, and the
gyro-kinematic calibration ages used by \citet{2024AJ....167..159L},
may not reproduce the rotation sequences of open clusters such as
Praesepe, the Hyades, and the Pleiades.  The \citet{Mamajek_2008}
calibration used by \citet{Reinhold_2015} does reproduce such
sequences for Sun-like stars.  However the
uncertainties determined using this approach are underestimates, because
they do not marginalize over
the intrinsic scatter in rotation periods present for stars of a fixed
mass and age.

@@

\begin{figure*}[!t]
  \begin{center}
    \leavevmode
    \subfloat{
    \includegraphics[width=.96\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000.pdf}
    }

	\vspace{-0.35cm}
    \subfloat{
    \includegraphics[width=.96\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000_preciseagesonly.pdf}
    }
  \end{center}
  \vspace{-0.66cm}
  \caption{{\bf Kepler's demographic cliff,} visible in the
  rotation-derived ages of stars (left) and planet hosts (middle) in
  the Kepler field.  The top row corresponds to all stars with
  temperatures of 3800--6200\,K for which we calculated rotation-based
  ages.  The opaque lines impose quality cuts on factors such as
  binarity, crowding, and the star's evolutionary state.  The bottom
  row selects only stars with temperatures of 4400-5400\,K, which have
  relatively precise ages near 2\,Gyr due to their fast spin-down.
  The statistical uncertainty for a mean
  individual star at 1, 2, and 3\,Gyr is shown, and is identical
  across each row.  Finally, the right panel compares the
  rotation-derived ages against star formation histories
  derived using CMD fitting.  Completeness in Kepler's
  $P$$_{\rm rot}$ detection sensitivity is near unity until
  $t$$\lesssim$3\,Gyr \citep{2022ApJ...937...94M}.
  \label{fig:hist_tgyro}
  }
\end{figure*}

@@

%\software{
%  astropy \citep{Astropy18},
%  matplotlib \citep{matplotlib},
%  numpy \citep{numpy},
%  scipy \citep{scipy},
%}
